An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-08-03 reports/manuscript.tex
Additional formatting changes (#35)
* Add Table 1 to manuscript file

* Update abstract and manuscript text

* Add word temp files to gitignore

* Remove a word temp file

* Fix typo in abstract

* Rerun pipeline

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
43 effects from 32 meta-analyses met our criteria for statistical certainty.
Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\))
We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
}

>>>>

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
43 effects from 32 meta-analyses met our criteria for statistical certainty.
Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\)).
We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
}
